% In this file you should put the actual content of the blueprint.
% It will be used both by the web and the print version.
% It should *not* include the \begin{document}
%
% If you want to split the blueprint content into several files then
% the current file can be a simple sequence of \input. Otherwise It
% can start with a \section or \chapter for instance.

\tableofcontents

\chapter{Introduction}

The plan is to formalise definitions from the L-functions and modular forms database (LMFDB) in
mathlib as well as creating some tactics to import the relevant data from the LMFDB into mathlib.
The LMFDB contains many objects of interest to mathematicians, many of which are still beyond what can
currently be formalised in mathlib. For this reason we will focus on three main areas,
namely number fields, elliptic curves and modular forms. In each of these areas we will formalise
the relevant definitions and import data from the LMFDB.

Our first main goals are to formalise relevant definitions used my the LMFDB to uniquely identify
objects in the database, i.e. the labels used by the LMFDB.

This is still a rough blueprint, generated from the information contained in the LMFDB. For now we have
roughtly organised the definitions by areas, with a background chapter containing definitions that are
needed but don't quite fit into the three main areas above.

\textbf{Warning}: This blueprint is still a work in progress. In places the LaTeX is not rendering correctly, but everything has a link back to
the LMFDB, so if in doubt, it is worth checking the definitions there. Also Many of the definitions are already formalised, and they should soon
have links to the relevant definitions in mathlib.

\input{background}
\input{NumberFields}
\input{ellipticcurves}
\input{modularforms}
